AD Target Gene Report

### 2020-01-24 code/02-Master.Rmd
Mod 7 Plots

  org = 'hsa'
  host = 'grch38.ensembl.org'
  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
  ds <- listDatasets(ensembl)[, "dataset"]
  ds <- grep(paste0("^", org), ds, value = TRUE)

@@

#Load Gene Set:
Genes <- read.table( paste0(config$filedir, '/genelists/', config$genelistfile ), header=F, sep='\t')

@@

```{r Module1, eval = T, include=T}
if( 1 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by IGAP SNP evidence')

@@

```{r Module2, eval = T, include=T}
if( 2 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Differential Expression evidence')

@@

```{r Module3, eval = T, include=T}
if( 3 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Differential Proteomic Expression evidence')

@@

```{r Module4, eval = T, include=T}
if( 4 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by eQTL evidence')

@@

```{r Module5, eval = T, include=T}
if( 5 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Coexpression Module evidence')

@@

```{r Module6, eval = T, include=T}
if( 6 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Module Cell-Type Enrichments evidence')

@@

```{r Module7, eval = T, include=T}
setwd( config$filedir )
if( 7 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Differential Expression evidence')

>>>>

  org = 'hsa'
  #host = 'grch38.ensembl.org'
  #"ensembl",dataset="hsapiens_gene_ensembl")
  #ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
  ensembl <- useMart("ensembl",dataset="hsapiens_gene_ensembl")
  ds <- listDatasets(ensembl)[, "dataset"]
  ds <- grep(paste0("^", org), ds, value = TRUE)

@@

#Load Gene Set:
Genes <- read.table( config$genelistfile , header=F, sep='\t')

@@

```{r Module1, eval = T, include=T}
if( 1 %in% config$modules ){
  writeLines(paste0('Modeling and ranking genelist ', config$genelistfile ,' by IGAP SNP evidence'))

@@

```{r Module2, eval = T, include=T}
if( 2 %in% config$modules ){
  writeLines(paste0( 'Modeling and ranking genelist ', config$genelistfile ,' by Differential Expression evidence'))

@@

```{r Module3, eval = T, include=T}
if( 3 %in% config$modules ){
  writeLines(paste0('Modeling and ranking genelist ', config$genelistfile ,' by Differential Proteomic Expression evidence'))

@@

```{r Module4, eval = T, include=T}
if( 4 %in% config$modules ){
  writeLines(paste0( 'Modeling and ranking genelist ', config$genelistfile ,' by eQTL evidence') )

@@

```{r Module5, eval = T, include=T}
if( 5 %in% config$modules ){
  writeLines(paste0( 'Modeling and ranking genelist ', config$genelistfile ,' by Coexpression Module evidence') )

@@

```{r Module6, eval = T, include=T}
if( 6 %in% config$modules ){
  writeLines(paste0( 'Modeling and ranking genelist ', config$genelistfile ,' by Module Cell-Type Enrichments evidence'))

@@

```{r Module7, eval = T, include=T}
setwd( config$filedir )
if( 7 %in% config$modules ){
  writeLines(paste0('Modeling and ranking genelist ', config$genelistfile ,' by Differential Expression evidence'))
